---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# where

<!-- badges: start -->
[![R-CMD-check](https://github.com/mdsumner/where/workflows/R-CMD-check/badge.svg)](https://github.com/mdsumner/where/actions)
[![CRAN status](https://www.r-pkg.org/badges/version/where)](https://CRAN.R-project.org/package=where)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of where is to specify a region simply as point (longitude,latitude) and a region around that. 

This package does absolutely nothing with this information, but other packages might (get where I'm going ...?). 

## Installation

You can install  the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("mdsumner/where")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(where)

## get me outta here
where()
```

Ok, get me somewhere specific. 

```{r somewhere}
where(156, 34, wh = 100000)  ## 100km either side of that location
```

---

## Code of Conduct

Please note that the where project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

